Time slice analyses

### 2017-09-19 analyses/02-time-slice-analyses.Rmd
Comment out installs

## The latest version of Claddis (on development on my own branch)
if(!require(Claddis)) install_github("TGuillerme/Claddis")
library(Claddis)

## The latest version of dispRity 
if(!require(dispRity)) install_github("TGuillerme/dispRity", ref = "master")
library(dispRity) 
```
<!-- TG: I've switched to master branch for the new functions -->

>>>>

## The latest version of Claddis (on development on TG branch)
## install_github("TGuillerme/Claddis")
library(Claddis)

## The latest version of dispRity on master branch
## install_github("TGuillerme/dispRity", ref = "master")
library(dispRity) 
```
